The Shape Matching Element Method for Meshless Animation of NURBs Models

### 2021-01-08 paper/sections/related.tex
done intro draft

\section{Related Work}
\subsection{Shape Matching Related Papers}
\begin{enumerate}
    \item \textit{Shape Matching} \cite{10.1145/1073204.1073216}: Meshless simulation by fitting a polynomial describing the shapes deformation using only the nodal values.
    \item \textit{Lattice Shape Matching} \cite{10.1145/1275808.1276480}: Voxelize model to construct a lattice of cubes. Use these lattice cubes to construct overlapping shape matching regions (just like clustered shape matching?). The original mesh is deformed using trilinear interpolation of lattice vertex positions.
    \item \textit{Robust Real-Time Deformation of Incompressible Surface Meshes} \cite{10.1145/2019406.2019438}: Shape matching on trimeshes with overlapping regions (clustered shape matching). Adds an additional volume preservation constraint. Position based dynamics approach to satisfying volume preservation.
    \item \textit{Shape-Up: Shaping Discrete Geometry with Projections} \cite{10.1111/j.1467-8659.2012.03171.x}: Shape constraints by least squares fitting (like in shape matching). They have some "proximity function" indicating distance to least-squares fit, then uses projection operators to minimize proximity function (pretty much just shape matching). 
    \item \textit{Shape Matching with Oriented Particles} \cite{10.1145/1964921.1964987}: More general form for shape matching, permitting wider range of motion. Also they use shape matching projection operators for skinning, much like we do. For each skinning point, they specify weights with up to 4 particles (each with their own projection operator)
    \item \textit{Fast Adaptive Shape Matching Deformations} \cite{10.5555/1632592.1632606}: Essentially same thing as Lattice Shape Matching, but instead they use an octree instead of a basic voxel grid for shape matching. It's not super significant to mention this paper, but it does make clear that much of the followup work after shape matching never didn't emphasize it's utility as a meshless boundary only method. They kept converting it to a mesh-based method!
    \item \textit{A Geometric Deformation Model for Stable Cloth Simulation} \cite{10.2312/PE/vriphys/vriphys08/039-046} Shape matching for cloth simulation.
\end{enumerate}

>>>>

\section{Related Work}

\begin{table*}[h]
    \caption{Algorithms for simulation of NURBS models. 
        %A $*$ indicates support for non-manifold meshes via preprocessing using Zhou et al.~\shortcite{Zhou:2016:MASG}. 
    ``Not Done'' denotes features that are not demonstrated in publication but are theoretically achievable. ``?'' denotes that the feature was not demonstrated or discussed in literature.
    \emph{Meshless} indicates whether the algorithm requires a volumetric mesh, 
    \emph{Boundary}  indicates whether the algorithm uses boundary degrees-of-freedom directly in the simulation
    \emph{Relaxed} indicates the algorithm supports relaxed modelling requirements and does not requiring fabrication quality inputs,
    \emph{Code} describes whether or not there is a publicly available implementation of the method.}
    \label{tbl:compare}
    \begin{center}
    \begin{tabular}{l c c c c c c c c}
     \textbf{Algorithm} & \textbf{Meshless} & \textbf{Boundary} & \textbf{Relaxed} & \textbf{Code} \\
     \hline 
     \rowcolor[HTML]{DAE8FC} 
     \textbf{X-CAD~\cite{}} & No (Cutcells) & No & No & No \\  
     \textbf{Ours~\cite{}} & Yes & Yes & Yes & Planned \\  
     \hline
    \end{tabular}
    \end{center}

    \end{table*}
\subsection{Shape Matching Related Papers}
\begin{enumerate}
    \item \textit{Shape Matching} \cite{10.1145/1073204.1073216}: Meshless simulation by fitting a polynomial describing the shapes deformation using only the nodal values.
    \item \textit{Lattice Shape Matching} \cite{10.1145/1275808.1276480}: Voxelize model to construct a lattice of cubes. Use these lattice cubes to construct overlapping shape matching regions (just like clustered shape matching?). The original mesh is deformed using trilinear interpolation of lattice vertex positions.
    \item \textit{Robust Real-Time Deformation of Incompressible Surface Meshes} \cite{10.1145/2019406.2019438}: Shape matching on trimeshes with overlapping regions (clustered shape matching). Adds an additional volume preservation constraint. Position based dynamics approach to satisfying volume preservation.
    \item \textit{Shape-Up: Shaping Discrete Geometry with Projections} \cite{10.1111/j.1467-8659.2012.03171.x}: Shape constraints by least squares fitting (like in shape matching). They have some "proximity function" indicating distance to least-squares fit, then uses projection operators to minimize proximity function (pretty much just shape matching). 
    \item \textit{Shape Matching with Oriented Particles} \cite{10.1145/1964921.1964987}: More general form for shape matching, permitting wider range of motion. Also they use shape matching projection operators for skinning, much like we do. For each skinning point, they specify weights with up to 4 particles (each with their own projection operator)
    \item \textit{Fast Adaptive Shape Matching Deformations} \cite{10.5555/1632592.1632606}: Essentially same thing as Lattice Shape Matching, but instead they use an octree instead of a basic voxel grid for shape matching. It's not super significant to mention this paper, but it does make clear that much of the followup work after shape matching never didn't emphasize it's utility as a meshless boundary only method. They kept converting it to a mesh-based method!
    \item \textit{A Geometric Deformation Model for Stable Cloth Simulation} \cite{10.2312/PE/vriphys/vriphys08/039-046} Shape matching for cloth simulation.
\end{enumerate}
